### 2024-02-24 dissertation-jhu/06-chapter-2.tex
published repository

\chapter{Chapter title goes here} \label{chap:chap-2}

% epigraph before chapter heading
\epigraphhead[0]{\epigraph{\enquote{Do not believe everything you see on the internet}}{-- Albert Einstein}}

\blindtext

### 2024-03-17 beamer/main.tex
aded beamer template

\def\BibFileName{template.bib}                  % name of BibLaTeX file with all the 
\def\FigurePath{figures}                        % subdirectory for the figure files

%%%%%%%%%%%%%%%%%%%%%%%% LaTeX CLASS AND THEME %%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[xcolor=dvipsnames,aspectratio=169]{beamer}
\useoutertheme[left]{sidebar}
\useinnertheme{rounded}
\usefonttheme[onlymath]{serif}                  % to use regular math font

\input{theme-preamble}
%%%%%%%%%%%%%%%%%%%%%% END LaTeX CLASS AND THEME %%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%% LaTeX PACKAGE AND SETTINGS %%%%%%%%%%%%%%%%%%%%%%
\usepackage{amsfonts,amssymb,amsmath,amsthm,autobreak, cancel,dsfont,mathtools,mathbbol,mathrsfs,siunitx,upgreek}

\usepackage[ruled]{algorithm2e}             % to manage algorithm environment
\usepackage[american]{babel}                % for different language typography

\usepackage[style=authoryear,autocite=footnote,backend=biber]{biblatex}

\usepackage{blindtext}

\usepackage{caption,subcaption}             % to manage captions
\usepackage{csquotes,epigraph,varwidth}     % for managing quotes
\usepackage{float}                          % to manage floating environment
\usepackage[T1]{fontenc}                    % for font encoding
\usepackage[bottom]{footmisc}               % footnote environment management
\usepackage{graphicx,wrapfig}               % to manage images
\usepackage{geometry}                       % to manage margins and others
\usepackage{hyperref}                       % for hyperlinks
\usepackage{listings}                       % to include codes

%%% table related packages
\usepackage{booktabs,longtable,makecell,multicol,multirow,tabularx,xltabular}

\usepackage[rightcaption]{sidecap}          % for sideway captions
\usepackage{tikz}                           % package for drawing

\hypersetup{colorlinks,linkcolor=,urlcolor=JHUPurple,citecolor=JHUPurple}
\addbibresource{\BibFileName}
\graphicspath{{\FigurePath/}}

%%%%%%%%%%%%%%%%%%% END LaTeX PACKAGE AND SETTINGS %%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%% LaTeX MACROS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\BLUE}{\textcolor{JHUDeepBlue}}
\newcommand{\PURPLE}{\textcolor{JHUPurple}}
\newcommand{\RED}{\textcolor{Red}}
\newcommand{\GREEN}{\textcolor{Green}}

%%%%%%%%%%%%%%%%%%%%%%% END LaTeX MACROS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%% DOCUMENT INFORMATION %%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title[About Beamer]
{Beamer template for Johns Hopkins University}
%\subtitle{Template made on customized theme}
\author[Doe]{John Doe}

\institute[JHU] {
    Affiliated position \\
    Name of department or institute \\
    \includegraphics[width=0.35\textwidth, trim={0.6in 0.35in 0.6in 0.3in},clip]{JHU_logo.pdf}
}

\date[VLC 2021]{Very Large Conference, April 2021}
%%%%%%%%%%%%%%%%%%%%%%%%%%% END DOCUMENT INFORMATION %%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\begingroup
\makeatletter
\setbeamertemplate{navigation symbols}{}
\setlength{\hoffset}{-.4\beamer@sidebarwidth}
\makeatother
\begin{frame}[plain]
    \titlepage
\end{frame}
\endgroup

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{First project}
\subsection{Introduction}
\begin{frame}{Highlighting text}

    In this slide, some important text will be \alert{highlighted} with JHU color because it's important. Please, don't \alert{abuse} it.

    \begin{block}{Remark}
        Sample text
    \end{block}

    \begin{alertblock}{Important theorem}
        Sample text in the red box
    \end{alertblock}

    \begin{examples}
        Sample text in the green box. The title of the block is ``Examples''.
    \end{examples}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Environment tests}
\begin{frame}{Enumerate and itemize test}
    \textbf{Enumerate environment with classic colors}
    \begin{enumerate}
        \item Hello, this is the \RED{first} point
        %
        \item This is my \GREEN{second} point
    \end{enumerate}

    \vspace{0.5in}

    \textbf{Itemize environment with JHU colors}
    \begin{itemize}
        \item This is a separate \BLUE{itemize} test 
        %
        \item Second point for the \PURPLE{separate} test
    \end{itemize}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Second project}
\subsection{Testing math environment}
\begin{frame}{Integration}
    Integration is also known as anti-derivative which represents the area under the curve. For indefinite integral, we should add a constant $C$ to the anti-derivative expressions.
    \begin{equation*}
        \int \exp(x) \ dx = \exp(x) + C
    \end{equation*}

    You can \textbf{\BLUE{boldface colors}} to emphasize even more\footnote{Hyperlinks will appear as \url{https://overleaf.com}}.

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Testing overlays}
\begin{frame}{More Lists}
    \begin{enumerate}[I]
    \item<1-> Point A\footnotemark
    \item<2-> Point B
    \begin{itemize}
    \item<3-> part 1
    \item<4-> part 2
    \end{itemize}
    \item<5-> Point C
    \item<6-> Point D
    \end{enumerate}

    \footnotetext{Second footnote testing here}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Overlaying math environment}
\begin{frame}{Maths Blocks}
    \begin{theorem}<1->[Pythagoras] 
        $ a^2 + b^2 = c^2$
    \end{theorem}
    \begin{corollary}<2->
        $ x + y = y + x  $
    \end{corollary}
    \begin{proof}<3->
        $\omega +\phi = \epsilon $
    \end{proof}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Third project}
\subsection{References}
\begin{frame}{References}
    \blindtext \footcite{einstein}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{document}

### 2024-03-17 beamer/theme-preamble.tex
aded beamer template

%%%%%%%%%%%%%%%%%%%%%%%%%%%%% JH colors %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%% following colors are defined based on: https://brand.jhu.edu/color
\definecolor{HeritageBlue}{RGB}{0,45,114}       % heritage blue
\definecolor{SpiritBlue}{RGB}{114,172,229}      % spirit blue

\definecolor{JHUPastle}{RGB}{0,155,119}         % pastle
\definecolor{JHUDeepBlue}{RGB}{0,114,206}       % deep blue

\definecolor{JHURed}{RGB}{166,25,46}            % red
\definecolor{JHUGreen}{RGB}{40,97,64}           % green

\definecolor{JHUViolet}{RGB}{81,40,79}          % violet
\definecolor{JHUPurple}{RGB}{161,90,149}        % purple
%%%%%%%%%%%%%%%%%%%%%%%%%%%%% JH COLORS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%% COLOR PALETTE SETTINGS %%%%%%%%%%%%%%%%%%%%%%%%%%
%%%% JHU color is used to set the palette for the beamer template

\setbeamercolor{palette primary}{bg=HeritageBlue,fg=white}
\setbeamercolor{palette secondary}{bg=HeritageBlue,fg=white}
\setbeamercolor{palette tertiary}{bg=HeritageBlue,fg=white}
\setbeamercolor{palette quaternary}{bg=HeritageBlue,fg=white}
\setbeamercolor{sidebar}{bg=White}
\setbeamercolor{palette sidebar primary}{bg=white,fg=HeritageBlue}
\setbeamercolor{palette sidebar secondary}{bg=white,fg=HeritageBlue}
\setbeamercolor{palette sidebar tertiary}{bg=white,fg=HeritageBlue}
\setbeamercolor{palette sidebar quaternary}{bg=white,fg=HeritageBlue}

\setbeamercolor{titlelike}{bg=HeritageBlue,fg=White}
\setbeamercolor{author}{fg=HeritageBlue}
\setbeamercolor{institute}{fg=HeritageBlue}
\setbeamercolor{date}{fg=HeritageBlue}

\setbeamercolor{frametitle}{bg=HeritageBlue,fg=White}
\setbeamercolor{frametitle continuation}{bg=HeritageBlue,fg=White}

\setbeamercolor{section in toc}{fg=HeritageBlue}        % TOC sections
\setbeamercolor{structure}{fg=HeritageBlue}             % itemize, enumerate, etc

\setbeamercolor{title in sidebar}{fg=HeritageBlue}
\setbeamercolor{author in sidebar}{fg=SpiritBlue}

\setbeamercolor{block title}{bg=HeritageBlue,fg=White}
\setbeamercolor{block body}{bg=HeritageBlue!10,fg=Black} 
\setbeamercolor{block title alerted}{bg=JHURed,fg=White}
\setbeamercolor{block body alerted}{bg=JHURed!10,fg=Black} 
\setbeamercolor{block title example}{bg=JHUGreen,fg=White}
\setbeamercolor{block body example}{bg=JHUGreen!10,fg=Black}

\setbeamercolor{footnote}{bg=White,fg=HeritageBlue}
\setbeamercolor{footnote mark}{bg=White,fg=HeritageBlue}

\setbeamercolor{alerted text}{fg=JHURed}

%%%%%%%%%%%%%%%%%%% END COLOR PALETTE SETTINGS %%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%% FONT SETTINGS %%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% size of the fonts in different environments of the beamer template
\setbeamerfont{title}{size=\Large}
\setbeamerfont{subtitle}{size=\large}
\setbeamerfont{author}{size=\normalsize}
\setbeamerfont{institute}{size=\scriptsize}
\setbeamerfont{frametitle}{size=\Large}

%%%%%%%%%%%%%%%%%%%%%%%%%% END FONT SETTINGS %%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%% FRAME TITLE, SIDEBAR, FOOTER SETTINGS %%%%%%%%%%%%%%%%%
\makeatletter
    \logo{\includegraphics[height=1cm]{JHU_shield.pdf}}
    \setlength{\beamer@headheight}{1cm}
\makeatother

\makeatletter
\setlength\beamer@sidebarwidth{0.75in}
  \setbeamertemplate{sidebar \beamer@sidebarside}%{sidebar theme}
  {
    \beamer@tempdim=\beamer@sidebarwidth%
    \advance\beamer@tempdim by -6pt%
    \insertverticalnavigation{\beamer@sidebarwidth}%
    \vfill
    \ifx\beamer@sidebarside\beamer@lefttext%
    \else%
      \usebeamercolor{normal text}%
      \llap{\usebeamertemplate***{navigation symbols}\hskip0.1cm}%
      \vskip2pt%
    \fi%
  }%
\makeatother

\setbeamertemplate{navigation symbols}
{\tiny\insertframenumber/\inserttotalframenumber}

%%%%%%%%%%%%% END FRAME TITLE, SIDEBAR, FOOTER SETTINGS %%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%% TOC SETTINGS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%% the next block of commands puts the table of contents at the 
%%%% beginning of each section and highlights the current section
\AtBeginSection[]
{
  \begin{frame}
    \frametitle{Table of Contents}
    \tableofcontents[currentsection]
  \end{frame}
}
%%%%%%%%%%%%%%%%%%%%%%%%% END TOC SETTINGS %%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2024-03-18 beamer/main.tex
updated repo

@@
 
+\def\AspectRatio{169}                           % aspect ratio of the presentation
+\def\FontPackage{helvet}                        % font package for presentation
+
+\def\BaseFontSize{11pt}                         % base font size for beamer
+\def\TitleFontSize{\Large}                      % title font size
+\def\SubtitleFontSize{\large}                   % subtitle font size
+\def\AuthorFontSize{\normalsize}                % author font size
+\def\InstituteFontSize{\footnotesize}           % institute font size
+\def\DateFontSize{\normalsize}                  % font size for the date on title page
+
+\def\TitleLogoSize{0.35\textwidth}              % width of the logo on the title page
+
+\def\FrameHeadHeight{1.0cm}                     % frame title height 
+\def\SidebarWidth{0.75in}                       % width of the siebar
+
+\def\FrameTitleFontSize{\Large}                 % frame title font size
+
 %%%%%%%%%%%%%%%%%%%%%%%% LaTeX CLASS AND THEME %%%%%%%%%%%%%%%%%%%%%%%%
-\documentclass[xcolor=dvipsnames,aspectratio=169]{beamer}
+\documentclass[xcolor=dvipsnames,aspectratio=\AspectRatio,\BaseFontSize]{beamer}
 \useoutertheme[left]{sidebar}
 \useinnertheme{rounded}
-\usefonttheme[onlymath]{serif}                  % to use regular math font
+% \usefonttheme[onlymath]{serif}                  % to use regular math font
 
@@
 
+\usepackage{helvet}
 \usepackage[ruled]{algorithm2e}             % to manage algorithm environment
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%% LaTeX MACROS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%% MATH SETTINGS AND MACROS %%%%%%%%%%%%%%%%%%%%%%%%
+
+\allowdisplaybreaks[1]
+\setcounter{MaxMatrixCols}{20}          % maximum columns in matrix = 20
+\numberwithin{equation}{section}        % eqn no begins with section no
+\newcommand{\dC}{$^{\circ}$C}           % degree celsius symbol
+\newcommand{\vect}[1]{\mathbf{#1}}      % boldface for vectors and tensors
+\DeclareMathOperator{\tr}{tr}           % trace of a matrix
+\DeclareMathOperator{\divg}{div}        % divergence of vector and tensor
+\DeclareMathOperator{\grad}{grad}       % gradient of vector and tensor
+
+%% these are just some examples; add more macros for your custom symbols
+
+%%%%%%%%%%%%%%%%%% END MATH SETTINGS AND MACROS %%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%% HIGHLIGHTING MACROS %%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%% END LaTeX MACROS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% these are just some examples; add more macros
+
+%%%%%%%%%%%%%%%%%%%% END HIGHLIGHTING MACROS %%%%%%%%%%%%%%%%%%%%%%%%%%
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \title[About Beamer]
-{Beamer template for Johns Hopkins University}
+{\LaTeX\ beamer template for Johns Hopkins University}
 %\subtitle{Template made on customized theme}
@@
     Name of department or institute \\
-    \includegraphics[width=0.35\textwidth, trim={0.6in 0.35in 0.6in 0.3in},clip]{JHU_logo.pdf}
+    \includegraphics[width=\TitleLogoSize,trim={0.6in 0.35in 0.6in 0.3in},clip]{JHU_logo.pdf}
 }
 
-\date[VLC 2021]{Very Large Conference, April 2021}
+\date[ALC 2024]{A Large Conference, March 2024}
 %%%%%%%%%%%%%%%%%%%%%%%%%%% END DOCUMENT INFORMATION %%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
+%%%% following code snippet is needed to remove the navigation symbols from the 
+%%%% title slide as well as to bring the frame at the center by offsetting for 
+%%% the sidebar.
 \begingroup
 \makeatletter
-\setbeamertemplate{navigation symbols}{}
-\setlength{\hoffset}{-.4\beamer@sidebarwidth}
+\setbeamertemplate{navigation symbols}{}            % removes page numbering
+\setlength{\hoffset}{-.425\beamer@sidebarwidth}     %
 \makeatother
